Table on stock change factors per clinate zone

### 2022-07-20 ResultNotebooks/results_SOCtable.Rmd
update of output scripts and figure

```{r load}
library(mrcommons)
library(mrvalidation)
library(mrsoil)
library(magpiesets)

scenarios <- c("rev19histManagement","rev18histManagement_ResAllom_2021_02_01")
outputdir <- "Output/"

#untar(paste0(getConfig("outputfolder"),"/",rev, "_h12_carbonbudget.tgz"), exdir="Data/histManagement", extras="--keep-newer-files ")

SoilCarbon <- read.magpie(paste0("Data/",scenarios[2],"/SoilCarbon.rds"))
Landuse    <- read.magpie(paste0("Data/",scenarios[2],"/Landuse.rds"))
```

@@

library(knitr)
library(stats)
library(reshape2)

years             <- findset("past")
climateIPCC       <- readRDS("Data/histManagement/IPCC_reduced.rds")

### calculating stock change factors
SOCDens           <- dimSums(SoilCarbon[,years,c("actualstate","naturalstate")], dim=3.3) 
SOCDens[,,"naturalstate.crop"] <- SOCDens[,,"actualstate.crop"]

CShare_ipcczone   <- dimSums(climateIPCC * SOCDens[,,"crop"][,,"actualstate"]   * Landuse[,years,"crop"], dim=1)/
                     dimSums(climateIPCC * SOCDens[,,"natveg"][,,"naturalstate"] * Landuse[,years,"crop"], dim=1)

getNames(CShare_ipcczone) <- gsub("_", " ", getNames(CShare_ipcczone))

SCF_table  <- data.frame(dcast(as.data.frame(collapseNames(CShare_ipcczone[,years,"naturalstate"])), 
                             Year ~ Data1, value.var="Value", row.names=years), row.names = "Year")
saveRDS(list(SCF_table = SCF_table), paste0(outputdir, "SFC_climatezone.rds"))

@@

climateIPCCr       <- readRDS("Data/histManagement/IPCC_reduced.rds")
climateIPCC        <- readRDS("Data/histManagement/IPCC.rds")

getNames(climateIPCC) <- c( "W-Temp Moist","W-Temp Dry","C-Temp Moist","C-Temp Dry","Polar Moist","Polar Dry","Boreal Moist",
                            "Boreal Dry","Tropical Montane","Tropical Wet","Tropical Moist", "Tropical Dry")

climateIPCC <- climateIPCC[,,c(5,7,3,1,6,8,4,2,9,11,10,12)]

magpie_coord <- toolGetMapping("magpie_coord.rda", type="cell")
climate2plot <- dimSums(climateIPCC*new.magpie("GLO",NULL,getNames(climateIPCC),c(1:12)), dim=3)
climate2plot <- merge(as.data.frame(climate2plot), data.frame(magpie_coord, Cell=c(1:59199)), by="Cell")

@@

map.world <- map_data("world")
world         <- ne_countries(scale = "medium", returnclass = "sf")
data(coastlineWorld)  
coastline.world <- data.frame(longitude=coastlineWorld[["longitude"]],latitude=coastlineWorld[["latitude"]])

blucols          <- brewer.pal(9, "Blues")[2:5]
viocols          <- brewer.pal(9, "Purples")[6:9]
redcols          <- brewer.pal(9, "Reds")[6:8]
orgcols          <- brewer.pal(9, "Oranges")[3]
cols <- c(blucols,viocols,redcols,orgcols)

ClimateZones <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(climate2plot, select=c("lon","lat","Value")), aes(x = lon, y = lat, fill = factor(Value))) +
    scale_fill_manual(name = "", 
                      values = cols, na.value = "white",
                      breaks= c(1,2,3,4,5,6,7,8,9,10,11,12),
                      labels = getNames(climateIPCC),
                      guide = guide_legend(
                        title.theme=element_text(size=legend_size),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = F,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
   scale_color_manual(values=cols) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          legend.text=element_text(size=legend_size),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7)),
          plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
          ) + guides(fill=guide_legend(nrow=2,byrow=FALSE))
ClimateZones 
ggsave(paste0(outputdir,"/Images/climatezones.png"), plot=ClimateZones , width = 20, height = 14, dpi = 300, units = "cm")
```

@@

MShare_ipcc <- LShare_ipcc <-  HShare_ipcc <- new.magpie("GLO",NULL,outer(c("IPCC2006","IPCC2019"),
                                                                          getNames(climateIPCCr), paste, sep="."))

MShare_ipcc <- add_dimension(MShare_ipcc, dim=3.2, nm="medium.invariant", add="input.year")
LShare_ipcc <- add_dimension(LShare_ipcc, dim=3.2, nm="low.invariant",    add="input.year")
HShare_ipcc <- add_dimension(HShare_ipcc, dim=3.2, nm="high.invariant",   add="input.year")

MShare_ipcc[,,"IPCC2006.medium"][,,"tropical_moist"]  <- "0.48"
MShare_ipcc[,,"IPCC2006.medium"][,,"tropical_dry"]    <- "0.58--0.64" 
MShare_ipcc[,,"IPCC2006.medium"][,,"temperate_moist"] <- "0.69"
MShare_ipcc[,,"IPCC2006.medium"][,,"temperate_dry"]   <- "0.80"

MShare_ipcc[,,"IPCC2019.medium"][,,"tropical_moist"]  <- "0.83"
MShare_ipcc[,,"IPCC2019.medium"][,,"tropical_dry"]    <- "0.92" 
MShare_ipcc[,,"IPCC2019.medium"][,,"temperate_moist"] <- "0.69--0.70"
MShare_ipcc[,,"IPCC2019.medium"][,,"temperate_dry"]   <- "0.76--0.77"

#Low input regime factor
LShare_ipcc[,,"IPCC2006.low"][,,"tropical_moist"]  <- "0.44"
LShare_ipcc[,,"IPCC2006.low"][,,"tropical_dry"]    <- "0.55--0.61" 
LShare_ipcc[,,"IPCC2006.low"][,,"temperate_moist"] <- "0.66"
LShare_ipcc[,,"IPCC2006.low"][,,"temperate_dry"]   <- "0.74"

LShare_ipcc[,,"IPCC2019.low"][,,"tropical_moist"]  <- "0.76"
LShare_ipcc[,,"IPCC2019.low"][,,"tropical_dry"]    <- "0.87" 
LShare_ipcc[,,"IPCC2019.low"][,,"temperate_moist"] <- "0.66--0.67"
LShare_ipcc[,,"IPCC2019.low"][,,"temperate_dry"]   <- "0.70--0.71"

#High input regime factor
HShare_ipcc[,,"IPCC2006.high"][,,"tropical_moist"]  <- "0.53"
HShare_ipcc[,,"IPCC2006.high"][,,"tropical_dry"]    <- "0.60--0.67" 
HShare_ipcc[,,"IPCC2006.high"][,,"temperate_moist"] <- "0.77"
HShare_ipcc[,,"IPCC2006.high"][,,"temperate_dry"]   <- "0.83"

HShare_ipcc[,,"IPCC2019.high"][,,"tropical_moist"]  <- "0.92"
HShare_ipcc[,,"IPCC2019.high"][,,"tropical_dry"]    <- "0.96" 
HShare_ipcc[,,"IPCC2019.high"][,,"temperate_moist"] <- "0.77--0.78"
HShare_ipcc[,,"IPCC2019.high"][,,"temperate_dry"]   <- "0.79--0.80"

CShare_ipcc <- mbind(LShare_ipcc,MShare_ipcc,HShare_ipcc)
getNames(CShare_ipcc) <- gsub("_", " ", getNames(CShare_ipcc))

comparison <- mbind(CShare_ipcc, 
                    round(add_dimension(setYears(collapseNames(CShare_ipcczone[,"y1990","naturalstate"]),NULL),
                                  nm="This Study.hist.1990",add="model.input.year"),2),
                    round(add_dimension(setYears(collapseNames(CShare_ipcczone[,"y2010","naturalstate"]),NULL),
                                  nm="This Study.hist.2010",add="model.input.year"),2))

#print(dimOrder(comparison[,,sort(getNames(comparison,dim=1))], c(2,1)))

comparison_table  <- data.frame(dcast(as.data.frame(collapseNames(comparison)), 
                           Data1 + Data2 + Data3 ~ Data4, value.var="Value", 
                            row.names=levels(as.data.frame(comparison)$Data1)))

colnames(comparison_table) <- gsub("\\.", " ", colnames(comparison_table))
colnames(comparison_table)[1:3] <- c("Source", "Input", "Year")

saveRDS(list(comparison_table = comparison_table), paste0(outputdir,"SFC_comparison.rds"))

@@

getwd()
table <- readRDS(paste0(outputdir,"/SFC_comparison.rds"))

save  <- kbl(table$comparison_table, latex = T, digit=2)%>%
            kable_styling(latex_options = c("scale_down","striped"), full_width = F)%>%
              row_spec(7:8, bold=TRUE)

save_kable(save, file="Output/Images/TableSCF_comparison.png")
```

>>>>

```{r load}
library(mrcommons)
library(mrvalidation)
library(mrcommons)
library(magpiesets)

outputdir <- "Output/"

rev         <- "rev30"
scen        <- "histManagement"

# untar(paste0(getConfig("outputfolder"),"/",rev, "_h12_carbonbudget.tgz"),
#       exdir="Data/histManagement", extras="--keep-newer-files ")

SoilCarbon <- readRDS(paste0("Data/", rev, scen, "/SoilCarbon.rds"))
Landuse    <- readRDS(paste0("Data/", rev, scen, "/Landuse.rds"))

@@

library(knitr)
library(stats)
library(reshape2)
library(Hmisc)

years             <- seq(1975, 2010, 5)
climateIPCCr      <- readRDS(paste0("Data/", rev, scen, "/IPCC_reduced.rds"))

### calculating stock change factors cropand weighted
SOCDens <- dimSums(SoilCarbon[, years, c("actualstate", "naturalstate")], 
                   dim = 3.3)
SOCDens[, , "naturalstate.crop"] <- SOCDens[, , "actualstate.crop"]

Cshare_cell       <- collapseNames(climateIPCCr * 
                       toolConditionalReplace(
                         SOCDens[, , "crop"][, , "actualstate"] /
                         SOCDens[, , "natveg"][, , "naturalstate"],
                         c("is.na()", "is.nan()", "is.infinite()"), 
                         c(NA, NA, NA)))

CShare_study      <- new.magpie("GLO", years,  
                          outer(getNames(climateIPCCr),
                                c("Q0p05", "Q0p5", "Q0p95"), 
                                paste, sep = "."))

cropMask  <- (Landuse[, years, "crop"] > 0.001)

for (zone in getNames(climateIPCCr)) {

  tempMMask <- setYears(
                 climateIPCCr[, rep(1, length(years)) , zone] == 1,
                 years) & cropMask

  for(y in years) {

    cropTempM <- Landuse[, y , "crop"][tempMMask[, y, ]]
    CShare_study[, y , zone] <- 
    Hmisc::wtd.quantile(Cshare_cell[, y, zone][tempMMask[, y, ]], 
                        cropTempM, 
                        probs = c(0.05, 0.5, 0.95))  
  }
}

getNames(CShare_study) <- gsub("_", " ", getNames(CShare_study))
getCells(CShare_study) <- "GLO"

SCF_table  <- as.data.frame(CShare_study)[-1]

saveRDS(SCF_table, paste0(outputdir, "SFC_climatezone+range.rds"))
```

@@

climateIPCCr <- readRDS(paste0("Data/", rev, scen, "/IPCC_reduced.rds"))
climateIPCC  <- readRDS(paste0("Data/", re, scen, "/IPCC.rds"))

getNames(climateIPCC) <- c("W-Temp Moist", "W-Temp Dry", "C-Temp Moist", 
                           "C-Temp Dry", "Polar Moist", "Polar Dry", 
                           "Boreal Moist",  "Boreal Dry", "Tropical Montane", 
                           "Tropical Wet", "Tropical Moist", "Tropical Dry")

climateIPCC <- climateIPCC[, , c(5, 7, 3, 1, 6, 8, 4, 2, 9, 11, 10, 12)]

magpie_coord <- toolGetMapping("magpie_coord.rda", type = "cell")
climate2plot <- dimSums(climateIPCC * 
                          new.magpie("GLO", NULL, 
                                     getNames(climateIPCC), 
                                     c(1:12)), 
                        dim = 3)
climate2plot <- merge(as.data.frame(climate2plot), 
                      data.frame(magpie_coord, Cell = c(1:59199)), by = "Cell")

@@

map.world <- map_data("world")
world         <- ne_countries(scale = "medium", returnclass = "sf")
data(coastlineWorld)
coastline.world <- data.frame(longitude = coastlineWorld[["longitude"]], 
                              latitude = coastlineWorld[["latitude"]])

blucols          <- brewer.pal(9, "Blues")[2:5]
viocols          <- brewer.pal(9, "Purples")[6:9]
redcols          <- brewer.pal(9, "Reds")[6:8]
orgcols          <- brewer.pal(9, "Oranges")[3]
cols <- c(blucols, viocols, redcols, orgcols)

ClimateZones <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(climate2plot, select = c("lon", "lat", "Value")), 
              aes(x = lon, y = lat, fill = factor(Value))) +
    scale_fill_manual(name = "",
                      values = cols, na.value = "white",
                      breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),
                      labels = getNames(climateIPCC),
                      guide = guide_legend(
                        title.theme = element_text(size = legend_size),
                        direction = "horizontal",
                        title.position = "top",
                        # I shift the labels around, the should be placed
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = FALSE,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
   scale_color_manual(values = cols) +
    theme(legend.position = "bottom",
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          legend.text = element_text(size = legend_size),
          rect = element_blank(),
          panel.background = element_rect(fill = "#F8F8FF", size = c(0.7, 0.7)),
          plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
          ) + guides(fill = guide_legend(nrow = 2, byrow = FALSE))
ClimateZones
ggsave(paste0(outputdir, "/Images/climatezones.png"), 
       plot = ClimateZones, width = 20, height = 14, dpi = 300, units = "cm")
```

@@

climateIPCCr <- readRDS(paste0("Data/", rev, scen, "/IPCC_reduced.rds"))

categories   <- c("IPCC2006.low", "IPCC2006.medium", "IPCC2006.high",
                  "IPCC2019.low", "IPCC2019.medium", "IPCC2019.high" )

CShare_ipcc <- new.magpie("GLO", NULL,  
                          outer(categories, 
                                getNames(climateIPCCr),
                                paste, sep = "."))

y2006m <- "IPCC2006.medium" 
y2006l <- "IPCC2006.low" 
y2006h <- "IPCC2006.high" 
y2019m <- "IPCC2019.medium" 
y2019l <- "IPCC2019.low" 
y2019h <- "IPCC2019.high"

# Medium input regime factor
CShare_ipcc[, , y2006m][, , "tropical_moist"]  <- 0.48
CShare_ipcc[, , y2006m][, , "tropical_dry"]    <- 0.58
CShare_ipcc[, , y2006m][, , "temperate_moist"] <- 0.69
CShare_ipcc[, , y2006m][, , "temperate_dry"]   <- 0.80

CShare_ipcc[, , y2019m][, , "tropical_moist"]   <- 0.83
CShare_ipcc[, , y2019m][, , "tropical_dry"]     <- 0.92
CShare_ipcc[, , y2019m][, , "temperate_moist"]  <- 0.70
CShare_ipcc[, , y2019m][, , "temperate_dry"]    <- 0.77

# Low input regime factor
CShare_ipcc[, , y2006l][, , "tropical_moist"]  <- round(0.48 * 0.92, 2)
CShare_ipcc[, , y2006l][, , "tropical_dry"]    <- round(0.58 * 0.95, 2)
CShare_ipcc[, , y2006l][, , "temperate_moist"] <- round(0.69 * 0.92, 2)
CShare_ipcc[, , y2006l][, , "temperate_dry"]   <- round(0.80 * 0.95, 2)

CShare_ipcc[, , y2019l][, , "tropical_moist"]   <- round(0.83 * 0.92, 2)
CShare_ipcc[, , y2019l][, , "tropical_dry"]     <- round(0.92 * 0.95, 2)
CShare_ipcc[, , y2019l][, , "temperate_moist"]  <- round(0.70 * 0.92, 2)
CShare_ipcc[, , y2019l][, , "temperate_dry"]    <- round(0.77 * 0.95, 2)

# High input regime factor
CShare_ipcc[, , y2006h][, , "tropical_moist"]  <- round(0.48 * 1.11, 2)
CShare_ipcc[, , y2006h][, , "tropical_dry"]    <- round(0.58 * 1.04, 2)
CShare_ipcc[, , y2006h][, , "temperate_moist"] <- round(0.69 * 1.11, 2)
CShare_ipcc[, , y2006h][, , "temperate_dry"]   <- round(0.80 * 1.04, 2)

CShare_ipcc[, , y2019h][, , "tropical_moist"]   <- round(0.83 * 1.11, 2)
CShare_ipcc[, , y2019h][, , "tropical_dry"]     <- round(0.92 * 1.04, 2)
CShare_ipcc[, , y2019h][, , "temperate_moist"]  <- round(0.70 * 1.11, 2)
CShare_ipcc[, , y2019h][, , "temperate_dry"]    <- round(0.77 * 1.04, 2)

getNames(CShare_ipcc) <- gsub("_", " ", getNames(CShare_ipcc))

CShare_study  <- as.magpie(readRDS(
                   paste0(outputdir, "SFC_climatezone+range.rds")))

CShare_median   <- collapseNames(CShare_ipcc[, , y2006m])
CShare_range    <- CShare_study[, "y2010", c("Q0p05", "Q0p5", "Q0p95")] 
CShare_median[] <- CShare_study[, "y2010", "Q0p5"] 
CShare_range    <- round(
                     add_dimension(
                       setYears(
                         CShare_range, 
                         NULL),
                       nm = "This Study (5th - 95th percentile).historical 2010 (5th - 95th percentile)", 
                       add = "model"), 
                     2)
CShare_median   <- round(
                     add_dimension(
                       setYears(
                         CShare_median, 
                         NULL),
                       nm = "This Study (5th - 95th percentile).historical 2010 (median)", 
                       add = "model"), 
                     2)

comparison <- mbind(CShare_ipcc,
                    CShare_median)

comparison_table  <- as.data.frame(collapseNames(comparison))[c(-1, -2, -3)]

range_table       <- as.data.frame(CShare_range)[c(-1, -2, -3)]                          
colnames(comparison_table) <- gsub("\\.", " ", colnames(comparison_table))
colnames(comparison_table)[1:4] <- c("Source", "Management", "Region", "Data")
colnames(range_table)[1:4]      <- c("Source", "Management", "Region", "Data")

saveRDS(list(comparison_table = comparison_table), 
        paste0(outputdir, "SFC_comparison.rds"))
```

@@

getwd()
table <- readRDS(paste0(outputdir, "/SFC_comparison.rds"))

save  <- kbl(table$comparison_table, latex = TRUE, digit = 2) %>%
            kable_styling(latex_options = c("scale_down", "striped"), full_width = FALSE) %>%
              row_spec(7:8, bold = TRUE)

save_kable(save, file = "Output/Images/TableSCF_comparison_new.png")
table
```

```{r table2boxplot, fig.height=3, fig.width=6}

#comparison_table
range_table <- dcast(range_table, Source + Management + Region ~ Data)

cols <- c("#648FFF", "#DC267F", "#FFB000")[3:1]

SCFTable <- 
  ggplot() + 
    geom_linerange(data = range_table,
                   aes(x = Region, ymin = Q0p05, ymax = Q0p95, color = Source),
                   position = position_nudge(x = 0.165), size = 0.6) +
    geom_point(data = comparison_table, 
               aes(y = Data, x = Region, group = Source, color = Source, shape = Management), 
               position = position_dodge(width = 0.5), 
               size = 2) +
    labs(y = "Stock Change Factor",
         x = "Climate Zone") +
    scale_color_manual(values = cols) +
    guides(shape = guide_legend(order = 2),col = guide_legend(order = 1)) +
    theme(rect = element_blank(),
                        axis.title.y = element_text(size = legend_size,
                                                   margin = margin(t = 0, r = 10, b = 0, l = 0, 
                                                                   unit = "pt")),
                        axis.title.x = element_text(size = legend_size,
                                                   margin = margin(t = 10, r = 0, b = 0, l = 0, 
                                                                   unit = "pt")))

ggsave(paste0(outputdir, "Images/SCF_comparison.png"), 
       plot = SCFTable, height = 8, width = 18, units = "cm", dpi = 300)
```
